---
title: "Spatial Data and Map Making Tutorial"
author: "Spencer Dakin Kuiper"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
subtitle: Salmon Watersheds Lab
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#libraries that are used in the demo 

libs = c("dplyr", "sf","terra", "tidyterra", "leaflet","bcmaps", "ggplot2", "geodata", "patchwork", "ggnewscale","scico","fishualize", "MetBrewer", "ggspatial")

#check if packages are installed 
install.packages(setdiff(libs, rownames(installed.packages())),repos = "http://cran.us.r-project.org")
library(dplyr)
library(sf)
library(terra)
library(tidyterra)
library(leaflet)
library(bcmaps)
library(ggplot2)
library(geodata)
library(patchwork)
library(ggnewscale)
library(ggspatial)
library(MetBrewer)
library(fishualize)
library(scico)
```

## Useful Packages

Below is a list of useful packages for making maps in r.

```{r packages, eval = FALSE, warning=FALSE, message=FALSE}
library(dplyr) #for data manipulation and stuff 
library(sf) #to read and process vector data 
library(terra) # to read and process raster data 
library(tidyterra) #useful tools for raster mapping 
library(tmap) #visualization package 
library(leaflet) #interactive mapping package 
library(bcdata) #access to the bc data catalog 
library(bcmaps) #access to common spatial data via bc data catalog 
library(ggplot2) # visualization package 
library(lidR) #used to read, process and visualize lidar data 
library(rnaturalearth) # used to download data from  natural earth 
library(rnaturalearthdata) # used to download data from  natural earth  
library(ggspatial) #useful functions for adding scale bars and north arrows 
library(geodata) #download geospatial data 
library(patchwork) #create inset maps and complex figures 
```

## Books and tutorials

This is my favourite and probably the best book for all things geospatial in R: <https://r.geocompx.org/>

These tutorials us raster data but is a good introduction <https://rspatial.org/>

This is a workshop for using Lidar data. It is more advanced but useful if you would like to learn: <https://tgoodbody.github.io/lidRtutorial/>

## Websites to download data from

<https://earthengine.google.com/>

<https://climatena.ca/>

<https://opendata.nfis.org/mapserver/nfis-change_eng.html>

<https://lidar.gov.bc.ca/>

<https://www.naturalearthdata.com/>

<https://catalogue.data.gov.bc.ca/>

## packages for colours

```{r packages for colours , eval = FALSE, warning=FALSE, message=FALSE}
library(MetBrewer)
library(viridis)
library(fishualize)
library(RColorBrewer)
library(scico)
```

```{r}
#Example colours 
MetBrewer::met.brewer(name = "VanGogh2")
fishualize::fishualize(option= "Oncorhynchus_mykiss")
scico::scico_palette_show()
```

# How to make a map

## Scenario

You just received a grant to study the effects of elevation gradients on salmon sightings. Like any good scientist you are going to start your research by making a study area map.

## Lets start by making a map of canada

First we need to download or read all of the required data

```{r Canada Map, warning=FALSE, message=FALSE}

##Download data directly from URL,using BC maps, geodata, and read in files from hardrive 

#Great Lakes 
url <- "https://www.sciencebase.gov/catalog/file/get/530f8a0ee4b0e7e46bd300dd"

dest <- "./_data/great_lakes.zip"

if (!file.exists(dest)) {
  download.file(url, destfile = dest, mode = "wb")
}

unzip_dir <- "./_data/great_lakes"

unzip(dest, exdir = unzip_dir)

great_lakes <- list.files(unzip_dir, pattern = "hydro.*\\.shp$", recursive = T, full.names = T) %>%
  purrr::map(vect) %>%
  purrr::map(aggregate) %>%
  vect() %>%
  project("epsg:3347")

data_dir = "./_data/"

# Get canadian provinces 

cad <- geodata::gadm("Canada", level = 1, path = data_dir)

#get other countries 
world <- geodata::world(path =data_dir) %>%
  project("epsg:3347")


# read in vancouver island shapfile 
study_area = vect("./_data/gilford_island.geojson")


#get BC 
bc = bc_bound()%>%
  vect()


```

Next lets start building our map. We will begin by adding all of the layers using the `geom_spatvector()` function.

```{r Canada Map Step 1, warning=FALSE, message=FALSE }

ggplot()+
  geom_spatvector(data = world)+
  geom_spatvector(data = cad ) +
  geom_spatvector(data = great_lakes) +
  geom_spatvector(data = bc ) 




```

Notice how even though we added all the layers we are still to zoomed out to see our study area? We can use the function `coord_sf()` to set limits in our map. But first we will programmatically determine the map extents in r using the `ext()` function. 

```{r Canada Map Step 2, warning=FALSE, message=FALSE}

cad_ext <- cad %>%
  project(world) %>% 
  ext()


ggplot()+
  geom_spatvector(data = world)+
  geom_spatvector(data = cad ) +
  geom_spatvector(data = great_lakes) +
  geom_spatvector(data = bc ) +
  coord_sf(xlim = c(cad_ext$xmin, cad_ext$xmax),
           ylim = c(cad_ext$ymin, cad_ext$ymax))


```

Good Job! Now we can add some color and a red box that shows the location of our study area. The `fill =` argument adds colour to the inside of the polygons, if we wanted to change the outline colour we could use `col =`. 

```{r Canada Map Step 3, warning=FALSE, message=FALSE}
# read in study area data 
study_area = vect("./_data/gilford_island.geojson")

study_ext = study_area %>%
  project("epsg:3347")%>%
  ext()


study_box = study_ext %>%
  vect("epsg:3347")


ggplot() +
  geom_spatvector(data = world, fill = "#a3aeb6") +
  geom_spatvector(data = cad , fill = "#c6c9ce") +
  geom_spatvector(data = great_lakes, fill = "#97afb9") +
  geom_spatvector(data = bc, fill = "#e5e5e5") +
  geom_spatvector(data = study_box, col = "red", fill = "#00000000", linewidth = 1) +
  coord_sf(xlim = c(cad_ext$xmin, cad_ext$xmax),
           ylim = c(cad_ext$ymin, cad_ext$ymax))
```

Now lets make some final adjustments to the theme and background colors and assign the map to an object called canadamap so that we can come back to it later. 

```{r Canada map final, warning=FALSE, message=FALSE}
canadamap = ggplot() +
              geom_spatvector(data = world, fill = "#a3aeb6") +
              geom_spatvector(data = cad , fill = "#c6c9ce") +
              geom_spatvector(data = great_lakes, fill = "#97afb9") +
              geom_spatvector(data = bc, fill = "#e5e5e5") +
              geom_spatvector(data = study_box, col = "red", fill = "#00000000", linewidth = 1) +
              coord_sf(xlim = c(cad_ext$xmin, cad_ext$xmax),
                       ylim = c(cad_ext$ymin, cad_ext$ymax))+
              theme_bw() +
              theme(panel.background = element_rect(fill = "#97afb9"),
                    axis.ticks = element_blank(),
                    axis.text = element_blank(),
                    plot.background = element_blank())
canadamap
```

Congratulations you have now made a map of Canada that shows the location of a study area on Vancouver island. In the next section we will create a map of Vancouver island.

## Mapping Rasters: Elevation of the study area

Lets start by getting a bit more data.

```{r Read in Data, warning=FALSE, message=FALSE}
#download and process the digital elevation model for the study area 
study_area_sf = study_area%>%
  st_as_sf()
dem = cded_terra(aoi = study_area_sf)
plot(dem)
plot(st_geometry(study_area_sf), add = T)
```

Good you now have a digital elevation model for the study area. Notice how the elevation model extends outside of the study area. Lets fix that.

```{r Mask dem, warning=FALSE, message=FALSE}
study_area_proj = study_area%>%
  project(dem) #rpoject the study area shapefile to the same crs as the dem

demcrop = mask(dem,study_area_proj)
plot(demcrop)

```

Much better. Now that we have an elevation model we can move into ggplot to further customize the map.

```{r Map Dem step 1, warning=FALSE, message=FALSE}
ggplot()+
  geom_spatraster(data = demcrop)

```

Lets adjust the colour and customize the legend.

```{r Map dem step 2, warning=FALSE, message=FALSE}
ggplot()+
  geom_spatraster(data = demcrop )+
  scale_fill_hypso_c(palette = "usgs-gswa2", name = "Elevation (m)", 
                     guide = guide_colourbar(direction = "horizontal", 
                                             order = 2,
                                             title.position = "top"), na.value = NA)
```

Good! Now lets make the elevation really pop by creating a hillshade for a 3d effect and adjusting the theme.

```{r Map dem step 3, warning=FALSE, message=FALSE}
slope <- terrain(demcrop, "slope", unit = "radians")
aspect <- terrain(demcrop, "aspect", unit = "radians")
hill <- shade(slope, aspect, 30, 270)

# normalize names
names(hill) <- "shades"

# Hillshading, but we need a palette
pal_greys <- hcl.colors(1000, "Grays")


ggplot()+
  geom_spatraster(data = hill, alpha = 1) +
  scale_fill_gradientn(colors = pal_greys,
                       na.value = NA,
                       guide = "none") +
  ggnewscale::new_scale_fill()+
  geom_spatraster(data = demcrop, alpha = 0.65 )+
  scale_fill_hypso_c(palette = "usgs-gswa2", name = "Elevation (m)", 
                     guide = guide_colourbar(direction = "horizontal", 
                                             order = 2,
                                             title.position = "top"), na.value = NA)+
  theme_void()
```

Next, because we got rid of the graticule and background using `theme_void()` we are going to add a north arrow, scale bar and some final layout changes.

```{r Map dem step 4, warning=FALSE, message=FALSE}
ggplot()+
  geom_spatraster(data = hill, alpha = 1) +
  scale_fill_gradientn(colors = pal_greys,
                       na.value = NA,
                       guide = "none") +
  ggnewscale::new_scale_fill()+
  geom_spatraster(data = demcrop, alpha = 0.65 )+
  scale_fill_hypso_c(palette = "usgs-gswa2", name = "Elevation (m)", 
                     guide = guide_colourbar(direction = "horizontal", 
                                             order = 2,
                                             title.position = "top", legend.position = "inside", legend.position.inside = c(0.9, 0.1)), na.value = NA,
                     breaks = c(0,1000,2000))+
  theme_void()+
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.9, 0.1))+
  ggspatial::annotation_north_arrow(location = "tl", which_north = "true",
                                    pad_x = unit(1, "in"), pad_y = unit(0.5, "in"),
                                    height = unit(2,"cm"), width = unit(2,"cm"),
                                    style = ggspatial::north_arrow_nautical(
                                      fill = c("grey40", "white"),
                                      line_col = "grey"
                                                                        ))+
  ggspatial::annotation_scale(
    location = "br",
    pad_x = unit(1.7, "in"), pad_y = unit(0.3, "in"),
    bar_cols = c("grey40", "white"),
    text_family = "Arial",
    width_hint = 0.3
  ) 
```

Now lets bring all of the techniques together and create a publication ready study area map show study plot locations on Vancouver island.

We will begin by creating plot locations.

```{r interactive map , warning=FALSE, message=FALSE}
study_plots = st_sample(study_area_sf, 10)%>%
  st_as_sf()%>%
  mutate(Plot_label = 1:10)


#lets plot them on an interactive map 
plots_latlon = study_plots %>%
  st_transform(crs = 4269)

leaflet()%>%
     addTiles()%>%
      addMarkers(data = plots_latlon, popup = as.character(plots_latlon$Plot_label))



```

Lets start by adding our study area and study plots to a map

```{r study area step 1 , warning=FALSE, message=FALSE}

ggplot()+
  geom_spatvector(data = study_area)+
  geom_sf(data = study_plots, aes(col = "Study Points"))


```

This time lets start by making it a bit more pretty right off the bat.

```{r study area step 2 , warning=FALSE, message=FALSE}
ggplot()+
  geom_spatvector(data = study_area)+
  geom_sf(data = study_plots, aes(col = "Study Points"), size = 2)+
  scale_color_manual(values = "grey20", labels = "Study Sites")+
  labs(color = NULL)+
  theme_bw()+
  theme(legend.key=element_rect(fill=NA))
  
```

Now its starting to look ok. Lets add a few more layers and reall make it sparkle.

```{r study area step 3 , warning=FALSE, message=FALSE}


ggplot()+
geom_spatvector(data = bc, fill = "#e5e5e5")+
  geom_spatraster(data = hill, alpha = 1) +
  scale_fill_gradientn(colors = pal_greys,
                       na.value = NA,
                       guide = "none") +
  ggnewscale::new_scale_fill()+
  geom_spatraster(data = demcrop, alpha = 0.75) +
  scale_fill_hypso_c(palette = "usgs-gswa2", name = "Elevation (m)", 
                     guide = guide_colourbar(direction = "horizontal", 
                                             order = 2,
                                             title.position = "top"), na.value = NA) +
  geom_spatvector(data = study_area, fill = NA)+
  geom_sf(data = study_plots, aes(col = "Study Points"), size = 2)+
  scale_color_manual(values = "grey20", labels = "Study Sites")+
  labs(color = NULL)+
  
  theme_bw()+
  theme(legend.key=element_rect(fill=NA))
  
```

Oh no, because we added new layers to the map we have changed the extent.Lets go ahead and create a study area extent object to fix this problem.

```{r study area step 4, warning=FALSE, message=FALSE}
study_ext_bc = study_area %>%
  project(bc)%>% #the map take the crs of the first layer 
  ext()

ggplot()+
geom_spatvector(data = bc, fill = "#e5e5e5")+
  geom_spatraster(data = hill, alpha = 1) +
  scale_fill_gradientn(colors = pal_greys,
                       na.value = NA,
                       guide = "none") +
  ggnewscale::new_scale_fill()+
  geom_spatraster(data = demcrop, alpha = 0.75) +
  scale_fill_hypso_c(palette = "usgs-gswa2", name = "Elevation (m)", 
                     guide = guide_colourbar(direction = "horizontal", 
                                             order = 2,
                                             title.position = "top"), na.value = NA) +
  geom_spatvector(data = study_area, fill = NA)+
  geom_sf(data = study_plots, aes(col = "Study Points"), size = 2)+
  scale_color_manual(values = "grey20", labels = "Study Sites")+
  labs(color = NULL)+
  coord_sf(xlim = c(study_ext_bc$xmin, study_ext_bc$xmax),
          ylim = c(study_ext_bc$ymin, study_ext_bc$ymax))+
  theme_bw()+
  theme(legend.key=element_rect(fill=NA))
```

Good job! Now lets make some final layout changes

```{r study area step 5 , warning=FALSE, message=FALSE}
study_area = ggplot()+
geom_spatvector(data = bc, fill = "#e5e5e5")+
  geom_spatraster(data = hill, alpha = 1) +
  scale_fill_gradientn(colors = pal_greys,
                       na.value = NA,
                       guide = "none") +
  ggnewscale::new_scale_fill()+
  geom_spatraster(data = demcrop, alpha = 0.75) +
  scale_fill_hypso_c(palette = "usgs-gswa2", name = "Elevation (m)", 
                     guide = guide_colourbar(direction = "horizontal", 
                                             order = 2,
                                             title.position = "top"), na.value = NA) +
  geom_spatvector(data = study_area, fill = NA)+
  geom_sf(data = study_plots, aes(col = "Study Points"), size = 2)+
  scale_color_manual(values = "grey20", labels = "Study Sites")+
  labs(color = NULL)+
  coord_sf(xlim = c(study_ext_bc$xmin, study_ext_bc$xmax),
          ylim = c(study_ext_bc$ymin, study_ext_bc$ymax))+
  theme_bw()+
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.85, 0.85),panel.background = element_rect(fill = "#97afb9"),
    legend.background = element_rect(fill = NA),
    legend.text = element_text(hjust = 0.5, size = 9),
    legend.title = element_text(hjust = 0.5),
    legend.key=element_rect(fill=NA),
    legend.spacing.y = unit(0,"cm"),
    
  )
study_area
```

Now look at all of that blank space in the corner of the map. If only we had a map of canada laying around so that people from all over the world reading our article could figure out where this is..... Oh wait...

```{r Final , warning=FALSE, message=FALSE}
#we can use the patchworks package to create an inset map 
Final = study_area + inset_element(canadamap, 0,0,0.4,0.4)

Final
```

Lastly, lets export the map with correct sizing. This can be journal specific but I generally default to the [elsevier](https://www.elsevier.com/about/policies-and-standards/author/artwork-and-media-instructions/artwork-sizing) sizing. For this map we want it to be a full page width and roughly a 3rd of a page tall.

```{r export, warning=FALSE, message=FALSE }
ggsave("./StudyAreaMap.jpeg", plot = Final, dpi = 300, units = "mm", width = 185, height = 150)
```
